\begin{thebibliography}{10}
  \bibitem{microservice} M. Villamizar, O. Garces, H. Castro, M. Verano, L. Salamanca, R. Casal- ´
  las, and S. Gil, “Evaluating the monolithic and the microservice architecture pattern to deploy web applications in the cloud,” in 2015 10th
  \bibitem{linatronic} Krones Linatronic 735,” Krones.com. [Online].
  Available: https://www.krones.com/de/produkte/maschinen/leerflaschen-inspektionsmaschine-linatronic-735.php. [Accessed: 16-Jan-2022].
  \bibitem{mlops} Y. Zhou, Y. Yu and B. Ding, "Towards MLOps: A Case Study of ML Pipeline Platform," 2020 International Conference on Artificial Intelligence and Computer Engineering (ICAICE), 2020, pp. 494-500, doi: 10.1109/ICAICE51518.2020.00102.
  \bibitem{dockergetstarted} Docker Overview,” Docs.docker.com. [Online].
  Available: https://docs.docker.com/get-started/overview/. [Accessed: 20-Jan-2022].
  \bibitem{dockerdeep}N. Poulton, “Docker,” in Docker Deep Dive: Zero to Docker in a single book: Nigel Poulton, 2020, pp. 12–13. 
  \bibitem{dockerstoragedriver} About storage drivers,” Docs.docker.com. [Online].
  Available: https://docs.docker.com/storage/storagedriver/. [Accessed: 20-Jan-2022].
  \bibitem{dockerbestpracticedockerfile} Best practices for writing Dockerfiles,” Docs.docker.com. [Online]. 
  Available: https://docs.docker.com/develop/develop-images/dockerfile\_best-practices/.[Accessed: 20-Jan-2022].
  \bibitem{hypervisorcontainer} R. Morabito, J. Kjällman and M. Komu, "Hypervisors vs. Lightweight Virtualization: A Performance Comparison," 2015 IEEE International Conference on Cloud Engineering, 2015, pp. 386-393, doi: 10.1109/IC2E.2015.74.
  \bibitem{kubernetes} Was ist Kubernetes?,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/.[Accessed: 20-Jan-2022].
  \bibitem{kubernetesdocker} Don't Panic: Kubernetes and Docker,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/blog/2020/12/02/dont-panic-kubernetes-and-docker/.[Accessed: 20-Jan-2022].
  \bibitem{kuberneteskomponenten} Kubernetes Komponenten,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/de/docs/concepts/overview/components/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetesnodekomponenten} Kubernetes Components,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/docs/concepts/overview/components/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetesnodes} Nodes,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/de/docs/concepts/architecture/nodes/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetespods} Pods,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/de/docs/concepts/workloads/pods/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetesobjects} Understanding Kubernetes Objects,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/docs/concepts/overview/working-with-objects/kubernetes-objects/.[Accessed: 21-Jan-2022].  
  \bibitem{kubernetesdeployment} Creating a Deployment,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/docs/concepts/workloads/controllers/deployment/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetesnigeldeployments} N. Poulton, “Kubernetes Deployments,” in The Kubernetes Book, 2021 edition, Nigel Poulton, 2021, pp. 76–78. 
  \bibitem{kubernetesservice} Service,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/docs/concepts/services-networking/service/.[Accessed: 21-Jan-2022].
  \bibitem{kubernetesingress}“Ingress,” Kubernetes. https://kubernetes.io/docs/concepts/services-networking/ingress/ (accessed Feb. 08, 2022).

  \bibitem{kubernetesingresscontroller}“Ingress Controllers,” Kubernetes. https://kubernetes.io/docs/concepts/services-networking/ingress-controllers/ (accessed Feb. 08, 2022).
  \bibitem{kubernetesingresscontrollerlayer}“Layer 4 and Layer 7 Load Balancing,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/k8s-in-rancher/load-balancers-and-ingress/load-balancers/ (accessed Feb. 08, 2022).
  \bibitem{kubernetesingressibm}“What is Kubernetes Ingress?,” Apr. 21, 2021. https://www.ibm.com/cloud/blog/kubernetes-ingress (accessed Feb. 08, 2022).


  \bibitem{Kuberneteschangemaster} Kubernetes (K8s). Kubernetes, 2022. Accessed: Feb. 10, 2022. [Online]. Available: https://github.com/kubernetes/kubernetes/blob/master/CHANGELOG/CHANGELOG-1.20.md\#urgent-upgrade-notes




  \bibitem{k3s} K3s - Lightweight Kubernetes. k3s-io.[Online]. Available: https://k3s.io. [Accessed: 07-Feb-2022].
  \bibitem{k3sarch} K3s - Lightweight Kubernetes. k3s-io.[Online]. Available: https://k3s.io. [Accessed: 20-Jun-2021].
  \bibitem{k3sgit} K3s - Lightweight Kubernetes. k3s-io.[Online]. Available: https://github.com/k3s-io/k3s. [Accessed: 07-Feb-2022].


  \bibitem{k3sAnforderung}“K3s Resource Profiling,” Rancher Labs. https://rancher.com/docs/k3s/latest/en/installation/installation-requirements/resource-profiling/ (accessed Feb. 11, 2022).
  \bibitem{pi4}“Raspberry Pi Documentation - Processors.” https://www.raspberrypi.com/documentation/computers/processors.html (accessed Feb. 11, 2022).


  \bibitem{k3sServerAgent} K3s - Lightweight Kubernetes. k3s-io.[Online]. Available: https://github.com/k3s-io/k3s/issues/1279. [Accessed: 07-Feb-2022].
  
  \bibitem{flannel} Cluster Networking,” https://kubernetes.io/. [Online]. 
  Available: https://kubernetes.io/docs/concepts/cluster-administration/networking/.[Accessed: 30-Jan-2022].
  \bibitem{rancher}“Overview,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/overview/ (accessed Feb. 10, 2022).
  
  \bibitem{AzureKubernetesService}S. Buchanan, J. Rangama, and N. Bellavance, 
  “Deploying and Using Rancher with Azure Kubernetes Service,” in Introducing Azure Kubernetes Service: A Practical Guide to Container Orchestration, Eds. Berkeley, CA: Apress, 2020, pp. 79-99.

  \bibitem{rancherKubeconfig}“Access a Cluster with Kubectl and kubeconfig,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/cluster-admin/cluster-access/kubectl/ (accessed Feb. 11, 2022).


  \bibitem{kubernetesAuthenticating}“Authenticating,” Kubernetes. https://kubernetes.io/docs/reference/access-authn-authz/authentication/ (accessed Feb. 10, 2022).
  \bibitem{rancherArchitecture}“Architecture,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/overview/architecture/ (accessed Feb. 10, 2022).

  \bibitem{rancherArchitectureRecommendations}“Architecture Recommendations,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/overview/architecture-recommendations/ (accessed Feb. 10, 2022).
  \bibitem{rancherAgents}“Rancher Agents,” Rancher Labs. https://rancher.com/docs/rancher/v2.5/en/cluster-provisioning/rke-clusters/rancher-agents/ (accessed Feb. 10, 2022).

\bibitem{ibmHybrid}“hybrid-cloud,” May 06, 2021. https://www.ibm.com/de-de/cloud/learn/hybrid-cloud (accessed Feb. 11, 2022).

%Microservice Section

\bibitem{BuildingMicroservicesNewman}S. Newman, Building microservices, 2nd ed. Sebastopol, CA: O’Reilly Media, 2021.

\end{thebibliography}